\section{Project Timeline}

Most of the internal project timeline is very flexible, owing to both the fact that the methodology used is Agile development, 
as well as that all team members are university students with many responsibilities outside this project. \\

The timeline itself is shaped by two strict deadlines: \\
(1) The SRS Document Delivery Date -- \textbf{2024/11/27} \\
(2) The Project Delivery Date -- \textbf{2025/04} (Day unspecified, sometime towards the middle or end of the month) \\

All the other timeline aspects work around these deadlines. \\

As of yet, there exists no strict timeline of other key deliverables, as this doesn't seem like something beneficial to our project organisation.
Instead, the project progress is consistently monitored, and the expected internal delivery times are adjusted based on the team availability and progress. \\

To ensure consistent and effective monitoring, and keeping in spirit with the principles of Agile Development, in addition to the strict deadlines, the timeline is also shaped by sprints and standup meetings. \\

The project timeline is split into 3-week sprints, fitting 4 sprints into the entirety of a single semester, meaning 8 sprints in total and potentially additional time over the break.
Each sprint has a clearly outlined set of goals that need to be achieved, and through the duration of the sprint, the goals are actively monitored and it is ensured that progress towards the goals is being made. \\

Each sprint can also be viewed as a series of time slots allocated for independent work, with standup meetings inbetween.
The standup meeting is aimed to occur daily, and is there mainly to ensure the team is on track and that the sprint goals are actually being worked towards.
The meeting also serves to make sure the team is consistently aware of everyone's time availability, as well as to ensure any potential blockers are addressed as soon as possible. \\

The complete project timeline is thus shaped by both the hard deadlines imposed by the external project assignment, and internal time organisation based around sprints.

